The effects of priming in human computation

### 2014-06-06 docs/publications/2014.05_PNAS/manuscript.tex
reame pnas2.tex -> manuscript

One difficulty with the notion of priming is that there appears to be no 
defensible notion of an ``unprimed state''.  A participant always approaches
a task from in \textit{some} state of mind.  This will be influenced by her
exposures prior to the experiment, which cannot be known by the experimenter.  
In our experiment, for example, we include a prior image set that is in some
sense ``neutral'', but it is by no means a control group. The particular 
images used would arguably produce different priming from another set that
was also apparently ``neutral''.

We avoid this difficulty by defining priming relatively, and speak of one
treatment being \textit{differently primed} from another.

@@

A final factor to consider is that, individuals who are in the same priming 
treatment will still in general produce different output for a task
due to the natural variance between people.  Therefore, we defined in relation 
to populations, not individuals.

With these considerations, we are ready to propose the definition.
Consider two populations of people $\mathcal{J}$ and $\mathcal{K}$, that 
produce respectively two populations of outputs 
$\mathcal{L}$ and $\mathcal{M}$ during the completion of a task $\mathcal{T}$:

@@

A consequence of this choice is that empirical measures of $\theta$ always
represent lower bounds on the theoretical value appearing in the definition.
As a result, a measured $\theta$ that is greater than zero directly 
supports the conclusion that two populations are differently 
primed, up to the statistical significance of the measurement.  However, if 
$\theta$ is not found to be statistically different from zero, one cannot 
directly
conclude that two populations are the same in priming.  Rather, the definition
admits the possibility that there exists some other $\mathcal{A}'$ capable of 
generating a measure of $\theta$ greater than zero. Interpreting a result
that $\mathcal{A}$ fails to achieve accuracy significantly better than 
chance depends on the capabilities of $\mathcal{A}$ and the state of the art
of classifier algorithms.

@@

The prior and posterior images sets both consist of five images. Workers had
to provide five labels for each image.  For the posterior image set we chose 
images that contain prepared meals and feature a prominent, identifiable 
culture (see \textbf{Fig. 1}).  We intended that the content of these images 
would tend elicit labels focusing food or culture (or both).

One of the prior image sets, which we call \textit{ambiguous}, was chosen to
be most similar to the posterior image set, and contains images of prepared
meals, but whose cultural features are less prominent and more difficult to
identify (see \textbf{Fig. 2}).  
The \textit{cultural} prior set features iconic cultural scenes, but no food 
at all (see \textbf{Fig. 3}).  Finally, images from
the \textit{ingredients} prior image set depict separated ingredients, but, 
like the ambiguous set, did not have prominent cultural features (see 
\textbf{Fig. 4}).  See the \textbf{Materials and Methods} section for further 
details.

\subsection*{Results}
\paragraph{The priming of all treatments was easily detectible.}
We test for priming effects using our definition proposed in the introduction,
implemented with a Naive Bayes classifier.  \textbf{Figure 5} shows
the classifier performance in distinguishing between different pairs of 
treatments based on workers' labels for the test images, and the corresponding
value for $\theta_\text{NB}$.

The classifier distinguishes the various treatments from one another (pairwise)
with high accuracy, confirming that both priming modalities 
(in-task and framing) were effective.  Remarkably, the classifier not only 
distinguishes treatments tending toward a different ``orientations'' 
(e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$, \textbf{Fig. 5A}), 
it also distinguishes workers from treatments of the \textit{same} 
orientation with high accuracy 
(e.g. $\textsc{cult}_{img}$ and $\textsc{cult}_{fund, img}$, \textbf{Fig. 5B}).
Clearly the algorithmic definition of priming and its implementation as 
$\theta_\text{NB}$ provides a sensitive means for detecting the presence of
primed populations.

Next we look at the degree to which labels from individual test images reveal 
priming.  It would stand to reason that, as workers proceed through 
the test images, the effects of priming might be ``washed out''.  
\textbf{Figure 6} shows the
performance of the Naive Bayes classifier when using the labels workers provide
for particular images.  This does show that, as we look to later test images, 
the treatments' difference in priming, $\theta_\text{NB}$, declines.  In future
work, we plan to investigate the dynamics of priming wash-out in greater 
detail.

\paragraph{Priming orients focus.} Having demonstrated differential 
priming, we investigate the \textit{nature} of the priming.  To this
end, we construct an ontology of all the labels attributed to
the test images.  The ontology is a directed acyclic graph of terms,
with directed edges drawn from abstractions toward instances.  For example,
our ontology contains the path \texttt{food} $\to$ \texttt{ingredients} $\to$ 
\texttt{vegetables} 
$\to$ \texttt{tomato}.  In general, each of these terms is a label that
occurred in the corpus of labels provided, but in some cases we added 
an abstraction when it was missing, to connect the ontology.  We provide more
detail about the construction of the ontology in the 
\textbf{Materials and Methods} section.

We put the abstract classes  \texttt{activity}, 
\texttt{adjective}, \texttt{culture}, \texttt{food}, and \texttt{thing} at 
the root of the ontology.  We promote \texttt{food} and \texttt{culture}
to the root of the ontology simply because of the prominence of food and 
culture-related labels in the corpus.  We acknowledge that food is a 
central aspect of culture, but we do not put \texttt{food} \textit{under} 
\texttt{culture}
(nor vice versa) because there are food-related labels that are culturally 
ambiguous (e.g. \texttt{bread}), and there are culture-related labels without 
a direct connection to food (e.g. \texttt{ganesha}).  The many words that are 
both food and culture-related (e.g. \texttt{dim sum}) receive an inbound edge 
(or path) from both \texttt{food} and \texttt{culture}.
This allows us to gauge effects on the orientation of workers' focus
with respect to the concepts of food and culture by simply counting the number 
of labels they provide that descend from \texttt{food} and \texttt{culture}.

\textbf{Figure 7} plots the composition of labels (fraction of culture- and 
food-oriented labels) for different treatments and images.  In 
panel \textbf{7A}, we can see that, before considering the effects of 
treatments, there is significant variance in the composition of the labels 
for different images due to inherent differences in their content.  For our 
purpose, we are interested in the systematic differences between 
the treatments.

In \textbf{Fig. 7B} we exhibit the composition of labels for the various 
treatments (aggregating together the labels for all images for a given 
treatment).  We can see that the treatments which expose workers to the
cultural image sets do elicit significantly more culture-oriented and fewer
food-oriented labels compared to the other treatments ($\alpha=0.05$).  It 
also appeas that all the $\textsc{ingr}_x$ treatments produce more 
food-oriented labels, but we cannot assert this at significance 
$\alpha = 0.05$.

The effect size, however, is somewhat small.  Since we observed that priming 
difference ``wears off'', it may be the case 
that aggregating label compositions for all images actually masks the effects. 
In \textbf{Fig. 7C}, we plot label compositions for only the first
image.  This reveals that, in labeling the first test image, workers in the
$\textsc{cult}_{img,x}$ were strongly influenced to favor culture- over 
food-oriented labels.  The effect was strong enough to essentially reverse 
the proportions of these labels compared to the other treatments.  
This shows that in-task priming effects can dramatically distort the results 
of human computation tasks.

We next inspect this effect longitudinally, that is, as a function of 
the test image.  To do so, we compute the \textit{excess cultural orientation} 
($\Delta_{cult}$) of
$\textsc{cult}_{img}$ relative to $\textsc{ambg}$ as follows: 
\begin{align}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
\end{align}
where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
counts food-oriented labels, and $N$ is the total number of labels in a 
treatment.  
Intuitively, this is intended to capture how much 
more culture-oriented $\textsc{cult}_{img}$ is than $\textsc{ambg}$.  
\textbf{Figure 8} plots $\Delta_{cult}$ as a function of test image, $i$. It
clearly shows the strong influence on the labels attributed to the first image,
but for later images this effect immediately drops below statistically 
measureable levels, while remaining always positive.

@@

We can then define the relative specificity of two treatments, 
$S(\mathcal{U},\mathcal{V})$ to be the average
relative specificity of workers drawn uniformly from the treatments.  
$\hat{S}({\mathcal{U}, \mathcal{V}})$ estimates this using the sample mean:

@@

Likewise, in panels \textbf{9B}, and \textbf{9C}, 
wherever we see significant differences in specificity, it turns out that
these differences appear to mainly be due to differences in food specificity,
as can be seen by comparing to panels \textbf{9E}, \textbf{9F}, \textbf{9H}, 
and \textbf{9I}.  In fact, looking to panels \textbf{9D}, \textbf{9E}, and 
\textbf{9F},
there are no significant differences in cultural specificity to speak of. 
Clearly, food and culture are not on equal footing.  Various psychological 
explanations are possible, and we explore these in the discussion below.

@@

\paragraph{In-task priming is strong.}  We expected that the funder names 
would overtly signal to workers that the requester was interested in a 
specific aspect of image content.  On the other hand, the we did not 
expect the prior image set, though enriched in certain content, to overtly signal interest.  In turn, we expected that a signal of intent would 
strongly affect how the workers approach the task.  Perhaps the most unexpected
result of this study is the finding that the prior image set influenced 
workers' focus (label orientation) and specificity far more strongly than did 
framing the task with the funder names.

@@

Randomized ordering and replication of tasks is one method to abate this issue.
But the requester could also include an initial set of tasks as a 
``tuning phase''.  During the tuning phase, workers would be primed in a 
controlled way, through exposure to tasks that had been specially picked to
orient worker focus in a useful manner.  Moreover, this phase could double as a
screening phase to select quality workers [***].

@@

\paragraph{Subtle priming effects can be detected with $\theta_\text{NB}$.}
While the Naive Bayes classifier is able to distinguish all treatment pairs,
many such pairs cannot be distinguished on the basis of label orientation and 
specificity 
(for example $\textsc{cult}_{fund}$ and $\textsc{ingr}_{fund}$).
One might expect, then, that $\theta_\text{NB}$
for the pair $\textsc{cult}_{fund}$ and $\textsc{ingr}_{fund}$, would be 
smaller than for, say, $\textsc{cult}_{img}$ and \textsc{ambg}.  
\textbf{Figure 5A} shows that this is not the case.  Thus, priming can be 
strong without generating the effects one might expect, and in many 
circumstances, such effects might go entirely undetected.  We believe this 
is a strong argument in support of using $\theta_\text{NB}$ to supplement 
methods designed to measure specific priming effects.

\paragraph{Priming did not affect cultural specificity.}
It was quite surprising that the effects on workers' specificity was 
essentially
confined to food-oriented labels, and that we observed no significant movements
in cultural specificity.   This might reflect the different roles
played by food and culture in the human lexicon.  This seems plausible when we 
consider the vital role of food on the one hand, and the bias in social 
cognition known as \textit{out-group homogeneity}\cite{Vala2012491,Ray2012387,Ishii2011159,Boldry2007157}.
Out-group homogeneity is a phenomenon whereby people perceive fewer 
differences between members of an outgroup than between members of their 
ingroup \cite{Boldry2007157}.  One manifestation is that people 
spend less time observing outgroup members when asked to make a character 
judgment \cite{Vala2012491}.  This phenomenon can be explained in terms of 
adaptiveness: social cognition regarding one's ingroup is more consequential
\cite{Vala2012491}.  Thus, it would not be surprising to find that people had 
less nuanced vocabulary for culture than for food, where a nuanced vocabulary 
would be of direct survival benefit.

@@

Even with the above explanations, is surprising that 
$\textsc{cult}_{img,x}$ is simultaneously induced to 
produce a higher quantity of culture-oriented labels but not a higher
specificity of culture-oriented labels.  Since effects on 
label composition were only appreciable for the first test image 
(see \textbf{Fig. 8}), we also
performed the specificity analysis restricting to labels from the first
test image (see \textbf{Fig. S1}).  But even focusing on the first test image
shows no significant increase in cultural specificity for 
$\textsc{cult}_{img,x}$.  Thus, we observe that priming effects on 
orientation of focus and label specificity do not necessarily correlate.

@@

Under our measure of similarity based on shared labels, our results show that
more specific labels are provided to the posterior images when the prior and
posterior image sets are more similar.
An appealing explanation for 
this is the notion of \textit{negative priming}, wherein the participant
becomes desensitized to stimuli that do not seem salient [***].  Thus, workers 
who have been shown successive images of prepared meals 
would be much less inclined to provide generic terms such as \texttt{food} or 
\texttt{meal} since these terms would no longer seem salient in the 
context of their priming treatment.

\paragraph{Priming for better HPU performance.}
Thus, if one seeks very nuanced sorting or labeling from human workers, 
we recommend assembling the HPUs in a hierarchical fashion, with the 
HPUs at the top of the hierarchy performing coarse sorting (or labeling), 
splitting objects into streams to be handled by HPUs performing more nuanced 
work.  To implement this for an
image-labeling task, one could first serve the images for coarse labeling,
then cluster the images based on the labels and a language model, and then 
reserve the images, ensuring that each HPU operates on images from a single 
cluster.  The more homogeneous that a cluster of images is in terms of 
content, the more one might gain by serving the cluster for another round of
labeling.

@@

\subsection*{Conclusion}
We demonstrated that in-task priming can have a strong effect.  
For an image labeling task, in-task priming was stronger in its effects on 
the orientation and specificity of labels than was the disclosure of funder 
names chosen to signal the requester's interest in specific content.
Employers on microtask platforms should 
beware that strong biases may be introduced by the very tasks they provide,
and further research into the nature of these effects is warranted.  At the 
same time, in-task priming might be exploited to improve task output, for 
example, to drive more (or less) nuanced responses.

We demonstrated that our algorithmic definition of priming, and its 
implementation as the measure $\theta_\text{NB}$ provide a sensitive,
general-purpose method for detecting priming.  Even when the expected effects 
on label orientation and specificity could not be detected, $\theta_\text{NB}$ 
was high.  $\theta_\text{NB}$ provides direct statistical evidence that 
populations have been affected by priming, even when the effects are not 
understood. With our proposed definition, we advocate a more general view of 
priming as a form of hysteresis.

@@

\textbf{AMT Tasks.} The task described in the \textbf{Experimental Setup}
section was served to 900 workers, who were uniformly randomly assigned to
treatments.  All treatments had at least 126 task completions.  To obtain 
uniformly sized treatments, we randomly selected 126 samples from each 
treatment. Workers were
only allowed to participate once and could not see the prior or posterior 
images, nor the funder names when previewing the task.

@@

\textbf{Statistical significance for relative specificity.}
We used \textbf{Eq.~\ref{eq:specificity}} to compute the relative specificity
of two treatments.  To analyze relative specificity statistically,
we first develop \textbf{Eq.~\ref{eq:specificity}} from an intermediate 
definition.  Let the specificity of a worker $u$ relative to a 
\textit{basis treatment} $\mathcal{V}$, denoted $S_V(u)$, to be the expected 
relative specificity between $u$ and a worker uniformly sampled from 
$\mathcal{V}$:

\begin{align}
	S_V(u) =  \text{E}_V\{s(u,V)\}, \quad V \in_R \mathcal{V},
		\label{eq:basis-specificity}
\end{align}
where $V$ is a random, uniformly sampled worker from $\mathcal{V}$.  We 
subscript the expectation operator with $V$ to indicate 
that the expectation is taken over the distribution of $V$.  Then, the 
relative specificity of two treatments, $S(\mathcal{U},{V})$, can be 
written as:
\begin{align}
	S(\mathcal{U},\mathcal{V}) = 
		\text{E}_U\{S_V(U)\}, \quad U \in_R \mathcal{U},
		\label{eq:treatment-specificity}
\end{align}
where $U$ is a uniformly sampled worker from $\mathcal{U}$.  This yields 
estimators for $S_V(u)$ and $S(\mathcal{U}, \mathcal{V})$, and their variances
as shown below (note that 
\textbf{Eq.~\ref{eq:treatment-specificity-estimator}} is
equivalent to \textbf{Eq.~\ref{eq:specificity}}):

\begin{align}
	\hat{S}_V(u) &= \frac{1}{|\mathcal{V}|} \sum_{v \in \mathcal{V}} s(u,v), 
		\label{eq:basis-specificity-estimator} \\
		\hat{S}(\mathcal{U},\mathcal{V}) 
			&= \frac{1}{|\mathcal{U}|} \sum_{u \in \mathcal{V}} S_V(u),
		\label{eq:treatment-specificity-estimator} \\
		\text{Var}_V\{\hat{S}_V(u)\} 
			&= \frac{1}{|\mathcal{V}|}\text{Var}_V\{s(u,V)\},
		\label{eq:basis-specificity-variance} \\
		\text{Var}_{U,V}\{\hat{S}(\mathcal{U},\mathcal{V})\} 
			&= \frac{1}{|\mathcal{V}|\cdot|\mathcal{U}|^2} 
			\sum_{u\in U}\text{Var}_V\{{s}(u,V)\}.
		\label{eq:treatment-specificity-variance}
\end{align}
$\text{Var}_V{s(u,V)}$ can be directly calculated as a sample variance, so
\textbf{Eq.~\ref{eq:basis-specificity-estimator}} through \textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypotheses:
\begin{align}
	\begin{matrix}
		\mathbf{H_0}: S(\mathcal{U}, \mathcal{V}) = 0 \\[0.5em]
		\mathbf{H_1}: S(\mathcal{U}, \mathcal{V}) \neq 0
	\end{matrix}
\end{align}

@@

\paragraph{Table 1.}
	Experimental treatments.  Workers were uniformly randomly
	assigned to one of the treatments listed above.  The full funder 
	names used were ``The Global Foundation
	for Cultural Recognition'' and ``The National Foundation for 
	Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
	priming images used are shown in \textbf{Figs. B}, \textbf{C}, and 
	\textbf{D}.

\paragraph{Figure 1.}
	Testing image set. These images were presented to all workers in the order 
	shown after the priming set of images.

\paragraph{Figure 2.}
	Ambiguous image set. These images were presented to workers from certain
	treatments (see \textbf{Table 1}) in the order shown.

>>>>

One difficulty with the notion of priming is that there appears to be no 
defensible notion of an ``unprimed state''.  A participant always approaches
a task in \textit{some} state of mind.  This will be influenced by her
exposures prior to the experiment, which cannot be known by the experimenter.  
In our experiment, for example, we include a prior image set that is in some
sense ``neutral'', but it is by no means a control group. The particular 
images used would arguably induce different priming than that induced by 
another set that was, in its own way, ``neutral''.
We avoid this difficulty by defining priming relatively, and speak of one
treatment being \textit{differently primed} from another.

@@

A final factor to consider is that, individuals who are in the same priming 
treatment will still in general produce different output for a task,
due to the natural variance between people.  Therefore, we define priming in 
relation 
to populations, not individuals.

With these considerations, consider two populations of people 
$\mathcal{J}$ and $\mathcal{K}$, that produce respectively two populations of 
outputs $\mathcal{L}$ and $\mathcal{M}$ during the completion of a task 
$\mathcal{T}$:

@@

A consequence of this choice is that empirical measures of $\theta$ always
represent lower bounds on the theoretical value appearing in the definition.
As a result, a measured $\theta$ that is greater than zero directly 
supports the conclusion that two populations are differently 
primed, up to the statistical significance of the measurement.  However, if 
$\theta$ is not found to be statistically different from zero, one cannot 
directly
conclude that two populations are the same in priming.  The definition
admits the possibility that there exists some other $\mathcal{A}'$ capable of 
generating a measure of $\theta$ statistically greater than zero. 
Interpreting a result
that $\mathcal{A}$ fails to achieve accuracy significantly better than 
chance depends on the capabilities of $\mathcal{A}$ and the state of the art
of classifier algorithm design.

@@

The prior and posterior images sets both consist of five images. Workers had
to provide five labels for each image.  For the posterior image set we chose 
images that contain prepared meals and feature a prominent, identifiable 
culture (see \textbf{Fig. 1}).  We intended that the content of these images 
would elicit labels focusing food or culture (or both).

One of the prior image sets, which we call \textit{ambiguous}, was chosen to
be very similar to the posterior image set, in the sense that it consists of
images of prepared meals.  However, the ambiguous image set was chosen such 
that its cultural features are less prominent and more difficult to identify 
(see \textbf{Fig. 2}).  
The \textit{cultural} prior set features iconic cultural scenes, but no food 
at all (see \textbf{Fig. 3}).  Finally, images from
the \textit{ingredients} prior image set depict separated ingredients, but, 
like the ambiguous set, were chosen to avoid prominent cultural features (see 
\textbf{Fig. 4}).  See the \textbf{Materials and Methods} section for further 
details.

\subsection*{Results}
\paragraph{The priming of all treatments was easily detectible.}
We test for priming effects using our definition proposed in the introduction,
implemented with a Naive Bayes classifier.  \textbf{Figure 5} shows
the classifier performance in distinguishing between different pairs of 
treatments based on workers' labels for the posterior images, and the corresponding
value for $\theta_\text{NB}$.

The classifier distinguishes the various treatments from one another (pairwise)
with high accuracy, confirming that both priming modalities 
(in-task and framing) were effective.  Remarkably, the classifier not only 
distinguishes treatments tending toward different ``orientations'' 
(e.g. $\textsc{cult}_{img}$ and $\textsc{ingr}_{img}$, \textbf{Fig. 5A}), 
it also distinguishes workers from treatments of the \textit{same} 
orientation with high accuracy 
(e.g. $\textsc{cult}_{img}$ and $\textsc{cult}_{fund, img}$, \textbf{Fig. 5B}).
Clearly the algorithmic definition of priming and its implementation as 
$\theta_\text{NB}$ provides a sensitive means for detecting the presence of
primed populations.

Next we look at the degree to which labels from individual posterior images reveal 
priming.  It would stand to reason that, as workers proceed through 
the posterior images, the effects of priming might be ``washed out''.  
\textbf{Figure 6} shows the
performance of the Naive Bayes classifier when using the labels workers provide
for particular images.  This does show that, as we look to later posterior images, 
the treatments' difference in priming, $\theta_\text{NB}$, declines.  In future
work, we plan to investigate the dynamics of priming wash-out in greater 
detail.

\paragraph{Priming orients focus.} Having demonstrated differential 
priming, we investigate the \textit{nature} of the priming.  To this
end, we construct an ontology of all the labels attributed to
the posterior images.  The ontology is a directed acyclic graph of terms,
with directed edges drawn from abstractions toward instances.  For example,
our ontology contains the path \texttt{food} $\to$ \texttt{ingredients} $\to$ 
\texttt{vegetables} 
$\to$ \texttt{tomato}. We provide more detail about the construction of the 
ontology in the \textbf{Materials and Methods} section.

The ontology allows us to algorithmically count the number of labels that are
of cultural orientation (\texttt{ganesha}),  food orientation
(\texttt{bread}), or both (\texttt{dim sum}).  We do this by counting the
number of labels having have inbound paths leading from the abstract clasess 
\texttt{culture} and/or \texttt{food}, which are present in the ontology.
\textbf{Figure 7} plots the composition of labels (fraction of culture- and 
food-oriented labels) for different treatments and images.  In 
panel \textbf{7A}, we can see that, before considering the effects of 
treatments, there is significant variance in the composition of labels 
for different images, probably due to inherent differences in their content.  
For our purpose, we are interested in the systematic differences between 
treatments.

In \textbf{Fig. 7B} we exhibit the composition of labels for the various 
treatments (aggregating together the labels for all images of a given 
treatment).  We can see that the treatments which expose workers to the
cultural image sets do elicit significantly more culture-oriented and fewer
food-oriented labels compared to the other treatments ($\alpha=0.05$).  It 
also appeas that all the $\textsc{ingr}_x$ treatments produce more 
food-oriented labels, but we cannot assert this at significance 
$\alpha = 0.05$.

The effect size, however, is somewhat small.  Since we observed that priming 
difference ``wears off'', it may be the case 
that aggregating label compositions for all images actually masks the effects. 
In \textbf{Fig. 7C}, we plot label compositions for only the first posterior
image.  This reveals that, in labeling the first posterior image, workers in 
$\textsc{cult}_{img,x}$ were strongly influenced to favor culture- over 
food-oriented labels.  The effect was strong enough to essentially reverse 
the proportions of these labels compared to the other treatments.  
This shows that in-task priming effects can dramatically distort the results 
of human computation tasks.

We next inspect this effect longitudinally, that is, as a function of 
the posterior image.  To do so, we compute the \textit{excess cultural orientation} 
($\Delta_{cult}$) of
$\textsc{cult}_{img}$ relative to $\textsc{ambg}$ as follows: 
\begin{align}
	\Delta_{cult}(i) = \frac{1}{N}\left[ \sum_{w\in\textsc{cult}_{img}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)
	- \sum_{w\in\textsc{ambg}} \left(N_{w,cult}^{(i)} - N_{w,food}^{(i)}\right)\right],
\end{align}
where $N_{w,cult}^{(i)}$ stands for the number of culture-oriented labels 
attributed by worker $w$ to image $i$, while $N_{w,food}^{(i)}$ similarly 
counts food-oriented labels, and $N$ is the total number of labels in a 
treatment.  
Intuitively, this is intended to capture how much 
more culture-oriented $\textsc{cult}_{img}$ is than $\textsc{ambg}$.  
\textbf{Figure 8} plots $\Delta_{cult}$ as a function of posterior image, $i$. 
This clearly shows the strong influence on the labels attributed to the first 
posterior image,
but for later images the effect immediately drops below statistically 
significant levels, while remaining always positive.

@@

We can then define the relative specificity of two treatments, 
$S(\mathcal{U},\mathcal{V})$, to be the average
relative specificity of workers drawn uniformly from the treatments.  
We obtain an estimator, $\hat{S}({\mathcal{U}, \mathcal{V}})$, using the 
sample mean:

@@

Likewise, in panels \textbf{9B}, and \textbf{9C}, 
wherever we see significant differences in specificity, it turns out that
these differences appear to mainly be due to differences in food specificity,
as can be seen by comparing to panels \textbf{9E}, \textbf{9F}, \textbf{9H}, 
and \textbf{9I}.  In fact, looking to panels \textbf{9D}, \textbf{9E}, and 
\textbf{9F},
there are no significant differences in cultural specificity to speak of. 
Clearly, food and culture are not on equal footing in the experiment.  Various 
psychological explanations are possible, and we explore these in the 
discussion below.

@@

\paragraph{In-task priming is strong.}  We expected that the funder names 
would overtly signal to workers that the requester was interested in a 
specific aspect of image content.  On the other hand, we did not 
expect the prior image set, though enriched in certain content, to overtly signal interest.  In turn, we expected that a signal of intent would 
strongly affect how the workers approach the task.  Perhaps the most 
unexpected result of this study is that the prior image set influenced label 
orientation and specificity far more than did framing the task by naming the
funder.

@@

Randomized ordering and replication of tasks is one method to abate this.
But the requester could also include an initial set of tasks as a 
``tuning phase''.  During the tuning phase, workers would be primed in a 
controlled way, through exposure to tasks that had been specially picked to
orient worker focus in a useful manner.  Moreover, this phase could double as a
screening phase to select quality workers [***].

@@

\paragraph{Subtle priming effects can be detected with $\theta_\text{NB}$.}
While the Naive Bayes classifier is able to distinguish all treatment pairs,
many such pairs cannot be distinguished on the basis of label orientation and 
specificity 
(for example $\textsc{cult}_{fund}$ and $\textsc{ingr}_{fund}$).
One might expect, then, that $\theta_\text{NB}$
for the pair $\textsc{cult}_{fund}$ and $\textsc{ingr}_{fund}$, would be 
smaller than for, say, $\textsc{cult}_{img}$ and \textsc{ambg}.  
\textbf{Figure 5A} shows that this is not the case.  Thus, priming can be 
strong without generating the effects one might expect, and in many 
circumstances, such effects might go entirely undetected.  We believe this 
is a strong argument in support of using $\theta_\text{NB}$ to determine 
whether priming has occurred, without making narrow assumptions about what the 
effects of priming will be.

\paragraph{Priming did not affect cultural specificity.}
It was quite surprising that the effects on workers' specificity was 
essentially
confined to food-oriented labels, and that we observed no significant movements
in cultural specificity.   This might reflect the different roles
played by food and culture in the human lexicon.  This seems plausible when we 
consider the vital role of food on the one hand, and the bias in social 
cognition known as \textit{outgroup homogeneity}\cite{Vala2012491,Ray2012387,Ishii2011159,Boldry2007157}.
Outgroup homogeneity is a phenomenon whereby people perceive fewer 
differences between members of an outgroup than between members of their 
ingroup \cite{Boldry2007157}.  One manifestation is that people 
spend less time observing outgroup members when asked to make a character 
judgment \cite{Vala2012491}.  This phenomenon can be explained in terms of 
adaptiveness: social cognition regarding one's ingroup is more consequential
\cite{Vala2012491}.  Thus, it seems plausible that a nuanced cultural 
vocabulary might be of limited advantage.  On the other hand,
the differences between food and poison can be nuanced indeed, and so it would
not be surprising to find that people have a more nuanced vocabulary for 
food than for culture.

@@

Even with the above explanations, is surprising that 
$\textsc{cult}_{img,x}$ is simultaneously induced to 
produce a higher quantity of culture-oriented labels but not a higher
specificity of culture-oriented labels.  Since effects on 
label composition were only appreciable for the first posterior image 
(see \textbf{Fig. 8}), we also
performed the specificity analysis restricting to labels from the first
posterior image (see \textbf{Fig. S1}).  But even when focusing on the first 
posterior image we see no significant increase in cultural specificity for 
$\textsc{cult}_{img,x}$.  Thus, we observe that priming effects on 
orientation of focus and label specificity do not necessarily correlate.

@@

Under our measure of similarity, our results show that
more specific labels are provided to the posterior images when the prior and
posterior image sets are more similar.
An appealing explanation for 
this is the notion of \textit{negative priming}, wherein the participant
becomes desensitized to stimuli that do not seem salient [***].  Thus, after 
workers had been shown successive images of prepared meals in the ambiguous
prior set, they would be much less inclined to provide generic terms such as 
\texttt{food} or 
\texttt{meal} to images in the posterior set, since these terms would no 
longer seem salient in the 
context of their priming treatment.

\paragraph{Priming for better HPU performance.}
Thus, if one seeks very nuanced sorting or labeling from human workers, 
we recommend assembling the HPUs in a hierarchical fashion, with the 
HPUs at the top of the hierarchy performing coarse sorting (or labeling), 
splitting objects into streams to be handled by HPUs performing more nuanced 
work.  To implement this for an
image-labeling task, one could first serve the images for coarse labeling,
then cluster the images based on the labels and a language model, and then 
re-serve the images, ensuring that each HPU operates on images from a single 
cluster.  The more ``homogeneous'' a cluster of images, the more one might gain
by serving the cluster for another round of labeling.

@@

\subsection*{Conclusion}
We demonstrated that in-task priming can have a strong effect.  
For an image labeling task, in-task priming was stronger in its effects on 
the orientation and specificity of labels than was the disclosure of funder 
names chosen to signal the requester's interest in specific content.
Employers on microtask platforms should 
beware that strong biases may be introduced by the very tasks they provide.
Further research into the nature of these effects is warranted.  At the 
same time, in-task priming might be exploited to improve task output, for 
example, to drive more (or less) nuanced responses.

We demonstrated that our algorithmic definition of priming, and its 
implementation as the measure $\theta_\text{NB}$ provide a sensitive,
general-purpose method for detecting priming.  Even when the expected effects 
on label orientation and specificity could not be detected, $\theta_\text{NB}$ 
was high.  $\theta_\text{NB}$ provides direct statistical evidence that 
populations have been affected by priming, even when the effects are not 
understood. Along with our proposed definition, we advocate a more general 
view of priming as a form of hysteresis.

@@

\textbf{AMT Tasks.} The task described in \textbf{Experimental Setup}
was served to 900 workers, who were uniformly randomly assigned to
treatments.  All treatments had at least 126 task completions.  To obtain 
uniformly sized treatments, we randomly selected 126 samples from each 
treatment. Workers were
only allowed to participate once and could not see the prior or posterior 
images, nor the funder names when previewing the task.

@@

\textbf{Statistical significance for relative specificity.}
We used \textbf{Eq.~\ref{eq:specificity}} to compute the relative specificity
of two treatments.  To analyze relative specificity statistically,
we first develop \textbf{Eq.~\ref{eq:specificity}} from an intermediate 
definition.  Let the specificity of a worker $u$ relative to a 
\textit{basis treatment} $\mathcal{V}$, denoted $S_V(u)$, be the expected 
relative specificity between $u$ and a worker uniformly sampled from 
$\mathcal{V}$:

\begin{align}
	S_V(u) =  \text{E}_V\{s(u,V)\}, \quad V \in_R \mathcal{V},
		\label{eq:basis-specificity}
\end{align}
where $V$ is a random, uniformly sampled worker from $\mathcal{V}$.  We 
subscript the expectation operator with $V$ to indicate 
that the expectation is taken over the distribution of $V$.  Then, the 
relative specificity of two treatments, $S(\mathcal{U},{V})$, can be 
written as:
\begin{align}
	S(\mathcal{U},\mathcal{V}) = 
		\text{E}_U\{S_V(U)\}, \quad U \in_R \mathcal{U},
		\label{eq:treatment-specificity}
\end{align}
where $U$ is a random, uniformly sampled worker from $\mathcal{U}$.  This 
yields 
estimators for $S_V(u)$ and $S(\mathcal{U}, \mathcal{V})$, and their variances
as shown below (note that 
\textbf{Eq.~\ref{eq:treatment-specificity-estimator}} is
equivalent to \textbf{Eq.~\ref{eq:specificity}}):

\begin{align}
	\hat{S}_V(u) &= \frac{1}{|\mathcal{V}|} \sum_{v \in \mathcal{V}} s(u,v), 
		\label{eq:basis-specificity-estimator} \\
		\hat{S}(\mathcal{U},\mathcal{V}) 
		&= \frac{1}{|\mathcal{U}|} \sum_{u \in \mathcal{V}} \hat{S}_V(u),
		\label{eq:treatment-specificity-estimator} \\
		\text{Var}_V\{\hat{S}_V(u)\} 
			&= \frac{1}{|\mathcal{V}|}\text{Var}_V\{s(u,V)\},
		\label{eq:basis-specificity-variance} \\
		\text{Var}_{U,V}\{\hat{S}(\mathcal{U},\mathcal{V})\} 
			&= \frac{1}{|\mathcal{V}|\cdot|\mathcal{U}|^2} 
			\sum_{u\in U}\text{Var}_V\{{s}(u,V)\}.
		\label{eq:treatment-specificity-variance}
\end{align}
$\text{Var}_V\{s(u,V)\}$ can be directly calculated as a sample variance.
\textbf{Equations \ref{eq:basis-specificity-estimator}} through 
\textbf{\ref{eq:treatment-specificity-variance}} provide enough information to test the hypotheses:
\begin{align}
	\begin{matrix}
		\mathbf{H_0}: S(\mathcal{U}, \mathcal{V}) = 0 \\[0.5em]
		\mathbf{H_1}: S(\mathcal{U}, \mathcal{V}) \neq 0
	\end{matrix}
\end{align}

@@

\paragraph{Table 1.}
	Experimental treatments.  Workers were uniformly randomly
	assigned to one of the treatments listed above.  The full funder 
	names used were ``The Global Foundation
	for Cultural Recognition'' and ``The National Foundation for 
	Nutritional Awareness''.  The ambiguous, cultural, and ingredients 
	prior image sets are shown in \textbf{Figs. 2}, \textbf{3}, and 
	\textbf{4}.

\paragraph{Figure 1.}
	Posterior image set. These images were presented to all workers after the 
	prior image set, in the order shown.

\paragraph{Figure 2.}
	Ambiguous prior image set. These images were presented to workers from 
	certain treatments (see \textbf{Table 1}) in the order shown.
